---
title: "Aesthetics"
output:
  pdf_document: default
  html_document: default
---

## Step 1: Import data

```{r}
hotel_bookings <- read.csv("hotel_bookings.csv")
```

## Step 2: See data

```{r look at data}
head(hotel_bookings)
```

```{r look at column names}
colnames(hotel_bookings)
```

## Step 3: Install and load the 'ggplot2' package

```{r loading and installing ggplot2, echo=FALSE, message=FALSE}
install.packages('ggplot2')
library(ggplot2)
```

## Step 4: Making a Bar Chart

```{r example chart}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = distribution_channel))
```


## Step 5: Diving deeper into bar charts

After exploring your bar chart, your stakeholder has more questions. Now they want to know if the number of bookings for each distribution type is different depending on whether or not there was a deposit or what market segment they represent. 

```{r pressure, echo=FALSE}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = distribution_channel, fill=deposit_type))
```

```{r pressure, echo=FALSE}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = distribution_channel, fill=market_segment))
```
## Step 6: Facets galore

After reviewing the new charts, your stakeholder asks you to create separate charts for each deposit type and market segment to help them understand the differences more clearly.

```{r creating a plot}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = distribution_channel)) +
  facet_wrap(~deposit_type)
```

```{r creating a plot}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = distribution_channel)) +
  facet_wrap(~market_segment)
```

```{r creating a plot}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = distribution_channel)) +
  facet_grid(~deposit_type)
```

```{r creating a plot}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = distribution_channel)) +
  facet_wrap(~deposit_type~market_segment)
```
