---
title: "Cleaning data"
---

## Step 1: Load packages

```{r}
install.packages("tidyverse")
install.packages("skimr")
install.packages("janitor")
```

Once a package is installed, you can load it by running the `library()` function with the package name inside the parentheses:

```{r}
library(tidyverse)
library(skimr)
library(janitor)
```
## Step 2: Import data

```{r}
bookings_df <- read_csv("hotel_bookings.csv")
```
## Step 3: See data

```{r}
head(bookings_df)
```

```{r}
str(bookings_df)
```

```{r}
glimpse(bookings_df)
```

```{r}
colnames(bookings_df)
```

```{r}
skim_without_charts(bookings_df)
```
## Step 4: Cleaning data


```{r}
trimmed_df <- bookings_df %>% 
  select(hotel, is_canceled, lead_time)
```

Rename the variable 'hotel' to be named 'hotel_type':
```{r}
trimmed_df %>% 
  select(hotel, is_canceled, lead_time) %>% 
  rename(hotel_type = hotel)
```

Combine the arrival month and year using the unite() function:

```{r}
example_df <- bookings_df %>%
  select(arrival_date_year, arrival_date_month) %>% 
  unite(arrival_month_year, c("arrival_date_month", "arrival_date_year"), sep = " ")
```

## Step 5: Mutate

```{r}
example_df <- bookings_df %>%
  mutate(guests = adults + children + babies)

head(example_df)
```

Calculate the total number of canceled bookings and the average lead time for booking.

```{r}
example_df <- bookings_df %>%
  summarize(number_canceled = sum(is_canceled),
            average_lead_time = mean(lead_time))

head(example_df)
```
